\vskip-0.6in \Large Political Uncertainty

### 2016-02-12 two-groups.tex
add foc for vote buyer A
fix A's foc
add FOCs for parameterized uncertainty to two-groups

			The FOC wrt to $b\left(\frac{1}{2}\right)$ is 
				\begin{equation}
					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
				\end{equation}
			Simplifying:
				\begin{equation}
					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
					\label{eq:logistic}
				\end{equation}
			Further math related to this equation is on Page~\pageref{eq:logistic2}.
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}
	\item Vote Buyer A
		\begin{itemize}
			\item Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
			  \begin{multline}
			    \max_{a\left(-\frac{1}{2}\right), a\left(0\right), a\left(\frac{1}{2}\right)} 
					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} +
					\frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Z_A}} + \\
					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
					\label{eq:obja}
				\end{multline}
				where 
				\begin{enumerate}
					\item $X_A = \alpha - b(0,a(0)) + a(0)$ 
					\item $Y_A = -\frac{\beta}{2} + \alpha - b\left(-\frac{1}{2},a\left(-\frac{1}{2}\right)\right)+ a\left(-\frac{1}{2}\right)$
					\item $Z_A = \frac{\beta}{2} + \alpha - b\left(\frac{1}{2},a\left(\frac{1}{2}\right)\right)+ a\left(\frac{1}{2}\right)$
				\end{enumerate}
		\end{itemize}
\end{enumerate}

@@

>>>>

			The FOC wrt to $b\left(\frac{1}{2}\right)$ is 
				\begin{equation}
					W_B \biggl[ \left( \frac{1}{1+e^{-X}} + \frac{1}{1+e^{-Y}} - 2 \frac{1}{1+e^{-X}} \frac{1}{1+e^{-Y}} \right) \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
				\end{equation}
			Simplifying:
				\begin{equation}
					W_B \biggl[ \frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
					\label{eq:logistic}
				\end{equation}
			Further math related to this equation is on Page~\pageref{eq:logistic2}.
			\item If we divide through by 2, the left side is the average minus the product
			\item Remember, I'm ignoring the constraints on WTP and non-negativity of bribes
		\end{itemize}
	\item Vote Buyer A
		\begin{itemize}
			\item Vote buyer A's objective function is identical in form to that of Vote buyer B (Expression~\ref{eq:objb}) 
			  \begin{multline}
			    \max_{a\left(-\frac{1}{2}\right), a\left(0\right), a\left(\frac{1}{2}\right)} 
					W_A \biggl[ \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} +
					\frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Z_A}} + \\
					\frac{1}{1+e^{-Y_A}} \frac{1}{1+e^{-Z_A}} - 2	\frac{1}{1+e^{-Z_A}} \frac{1}{1+e^{-X_A}} \frac{1}{1+e^{-Y_A}} \biggr] - \sum_{j\in \left\{-\frac{1}{2}, 0,\frac{1}{2}\right\}} a(j)
					\label{eq:obja}
				\end{multline}
				where 
				\begin{enumerate}
					\item $X_A = \alpha - b_0(\bm{a},W_B,\al,\beta) + a_0$ 
					\item $Y_A = -\frac{\beta}{2} + \alpha - b_{-.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{-.5}$
					\item $Z_A = \frac{\beta}{2} + \alpha - b_{.5}\left(\bm{a},W_B,\al,\beta\right)+ a_{.5}$
				\end{enumerate}
				with $\bm a = \left(a_{-.5},a_0,a_{.5} \right)$
			\item Vote Buyer A's first order condition with respect to $a_0$ is more complicated because of the dependencies on $\bm a$ (should probably double check this, but it makes sense)
			 \begin{multline}
					 \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-Y}}{\left[1+e^{-Y}\right]^2} \frac{\partial b_{-.5}}{\partial a_0} + \\ 
					\frac{e^{-X} + e^{-Y}}{\left(1+e^{-X}\right)\left(1+e^{-Y}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2}\frac{\partial b_{.5}}{\partial a_0} + \\
					\frac{2+e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left[1+e^{-X}\right]^2}\left[1 - \frac{\partial b_0}{\partial a_0} \right] = \frac{1}{W_A}
					\label{eq:focA}
				\end{multline}
		\end{itemize}
\end{enumerate}

@@

\newpage
\section{Parameterizing uncertainty that varies by legislator}
\label{sec:uncert}
I'm going to start by changing the uncertainty for just one legislator when there is just one vote buyer (B). I will do this for the legislator at position $-0.5$, which corresponds to $Y$. The FOCs become, for $Z$ (similarly for $X$, and from Equation~\ref{eq:logistic})
	\begin{equation}
		W_B \biggl[ \frac{e^{-X} + e^{-\frac{Y}{s_{-.5}}}}{\left(1+e^{-X}\right)\left(1+e^{-\frac{Y}{s_{-.5}}}\right)} \frac{e^{-Z}}{\left[1+e^{-Z}\right]^2} \biggr]  = 1
	\end{equation}
	And for $Y$
  \begin{equation}
		W_B \biggl[ \frac{e^{-X} + e^{-Z}}{\left(1+e^{-X}\right)\left(1+e^{-Z}\right)} \frac{e^{-\frac{Y}{s_{-.5}}}}{s_{-.5}\left[1+e^{-\frac{Y}{s_{-.5}}}\right]^2} \biggr]  = 1
	\end{equation}
